Active Learning : From Blackbox To Timed Connectors

### 2016-01-09 paper/paper.tex
.

\begin{figure}[h]
  \begin{center}
    \input{./images/pmmfifo.tex}
  \end{center}
  \caption{PMM-based Semantics of FIFO, where $\Sigma=\{a,b\}$}
  \label{fig:pmmfifo}
\end{figure}

@@

\subsection{Perfomance Optimization}

@@

\section{Case Studies}
\subsection{Alternator}
\subsection{Timed TODO}

>>>>

\todo{modify this image}
\begin{figure}[h]
  \begin{center}
    \input{./images/pmmfifo.tex}
  \end{center}
  \caption{PMM-based Semantics of FIFO, where $\Sigma=\{a,b\}$}
  \label{fig:pmmfifo}
\end{figure}

@@

\subsection{Perfomance Optimization}
In the learning algorithm, the most time-consuming operations are membership queries and
equivanlence queries.

\todo{analysis table}

@@

\section{Experiments}
Both \emph{Reo Coordination Models} and \emph{Adapted L* Algorithm} are implemented in Golang.
\todo{cite}
Golang (or Google Go) is a rising programming language started by Google Inc. The language is widely
known for its elegant design and impressive efficiency. Moreover, the concurrency model of Golang
comes from CSP\cite{DBLP:books/ph/Hoare85}. As a channel-based model, CSP shares a similar idea with
Reo and makes our implementation much more natural.

We have programmed Reo channels as a new package in Golang. The package is well-written for not only
formal verification but also practical use.

All the following experiments are coded under Golang \emph{1.2.1} and executed on a laptop with 8GB
of RAM and a Core i7-3630 CPU.

\subsection{Case Studies}
\subsection{Performance Optimization}
As a well-known learning algorithm, L* has proved its efficiency in models without time.
However, when dealing with timed connectors, the algorithm failed to meet our expectation.

\begin{table}[h]
  \renewcommand{\arraystretch}{1.3}
  \caption{Time-Cost Analysis}
  \label{tabel:timecost}
  \centering
  \begin{tabular}{l||rrr}
    \hline
    & FIFO & Alternator & Gate \\
    \hline\hline
    Membership Query(s) & 41.571 & 126.468 & 169.161 \\
    Hypothesis Query(s) & 0.001 & 0.003 & 0.004 \\
    Total Time(s) & 41.715 & 165.114 & 247.098\\
    Membership Query(\%) & 99.6 & 76.6 & 68.5\\
    \hline
  \end{tabular}
\end{table}

As shown in Table \ref{tabel:timecost}, time comsumption mainly comes from membership queries.
Since time is involved in our model, it's inevitably that simulation takes time to behave normally.
Even worse, since our models are treated as blackbox, there's little room for optimization. The only
way to reduce time cost is trying not to call the simulation process. Basic ideas are listed as
follows:

\begin{itemize}
  \item When constructing \emph{Obs} tables, there are lots of redundant calls to membership
    queries. For example, a sequence with prefix 'aa' and suffix 'b' is exactly same as another one
    with prefix 'a' and suffix 'ab'.
  \item Simulation on mealy machines can provide multi-step output. Consequently, if we has
    simulated an 'abc' sequence, there's no reason to perform simulation on an 'ab' sequence.
\end{itemize}

To reduce these repeated simulation, we use a cache to save all simulation results. 
\begin{table}[h]
  \renewcommand{\arraystretch}{1.3}
  \caption{Reduction of Membership Queries}
  \label{tabel:cacheoptimization}
  \centering
  \begin{tabular}{l||rrr}
    \hline
    & FIFO & Alternator & Gate \\
    \hline\hline
    Before & 41.571 & 126.468 & 169.161 \\
    After & 41.571 & 126.468 & 169.161 \\
    \hline
  \end{tabular}
\end{table}
